Check experimental design

### 2021-10-18 analysis/01_experimental-design.Rmd

# Interact-code the design

We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need a specific intercept-only design with each of the needed interactions.

```{r interact-design, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
interact_design <- as.data.frame(design)
for(i in 4:ncol(interact_design)) {
  interact_design[,i] <- as.factor(interact_design[,i])
}

# Rename the variables.
colnames(interact_design)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")

# Use dummy_cols() to get a dummy-coded version of all the attribute levels.
interact_design <- dummy_cols(
  interact_design, 
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = FALSE,
  remove_selected_columns = TRUE
)

# Rename the dummy-coded variables.
colnames(interact_design)[4:21] <- c(
  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
)

@@

interact_design %>% 

@@

  # Drop first levels and the nottransp helper variable.
  select(-c(contains("1"), nottransp))

# Save interact-coded design output
write.csv(interact_design, here("data", "derived_data", "interact_design.csv"))
```

>>>>

# Interactions

We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specific each of the needed interactions.

```{r interactions, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
interactions <- as.data.frame(design)
for(i in 4:ncol(interactions)) {
  interactions[,i] <- as.factor(interactions[,i])
}

# Rename the variables.
colnames(interactions)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")

# Use dummy_cols() to get a dummy-coded version of all the attribute levels.
interactions <- dummy_cols(
  interactions, 
  select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
  remove_first_dummy = FALSE,
  remove_selected_columns = TRUE
)

# Rename the dummy-coded variables.
colnames(interactions)[4:21] <- c(
  str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
  str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
)

@@

interactions <- interactions %>% 

@@

  # Drop the design and the nottransp helper variable.
  select(-c(org1:gov_rel3, nottransp))

# Save interact-coded design output
write.csv(interactions, here("data", "derived_data", "interactions.csv"))
```
